---
output: github_document
always_allow_html: true
---

# Sheffield Methods Institute: Custom `xaringan` slide decks

These are custom slide decks for the Sheffield Methods Institute in University of Sheffield branding. A preview of the slide deck along with some of the more useful but lesser-known features of `xaringan`/`react`'s CSS classes are included. It makes extensive use of `xaringanthemer` and `xaringanExtra` packages. 

This slide deck includes a custom top-only banner header in both violet and midnight black at 90% opacity (dark grey) (found in `insert-header-violet.html` and `insert-header-grey.html`), some custom CSS classes (`.middle-left[]` and `.middle-right[]`) to enable independent vertical centering of `.pull-left[]` and `.pull-right[]` style slides, as well as some custom 1/4:3/4 style column splits, text resizing classes.

A live version of the templates can be viewed here:

* Violet: [calumwebb.co.uk/pres/smi-slides-demo/violet/](https://calumwebb.co.uk/pres/smi-slides-demo/violet/)
* Grey: [calumwebb.co.uk/pres/smi-slides-demo/grey/](https://calumwebb.co.uk/pres/smi-slides-demo/grey/)


```{r, echo = FALSE}

library(htmltools)

image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,...)
    )
}

image_link("images/slides-preview-violet.png", url = "https://calumwebb.co.uk/pres/smi-slides-demo/violet/", width = "100%")

```

```{r, echo = FALSE}

library(htmltools)

image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,...)
    )
}

image_link("images/slides-preview-grey.png", url = "https://calumwebb.co.uk/pres/smi-slides-demo/grey/", width = "100%")

```
